Implementing simplified INLA into `aghq`

### 2022-10-12 src/dev_sinla/sinla.Rmd
Work on making the LHS vs RHS check better, and remove it the second time (they're essentially the same)

```{r}
input_param <- param
```

For the `phi_prev` parameters, we want to be using the `mean` that we previously computed, then evaluating everything using `f`.
We multiply by -1 because `f$fn` gives the negative log-likelihood, and we want just the log-likelihood:

```{r}
input_param$phi_prev <- mean
numer <- -1 * f$fn(unlist(input_param))
numer
```

Then for the denominator, it should be as follows:

```{r}
denom <- 0.5 * (determinant(Q, logarithm = TRUE)$modulus - (nrow(Q) * log(2 * pi)))
denom
```

Note that we use `determinant` on the log-scale as it is more numerically stable than e.g. `log(det(...))`.
On the log-likelihood scale, the number we get is:

```{r}
numer - denom
```

@@

```{r}
-1 * h$fn(input_param[c("beta_prev", "log_sigma_phi_prev")])
```

@@

## Reproducing output from `obj`

As above, we should be able to reproduce the output of `obj$fn` using the mean and precision matrix, together with the function `f`.
Recall that `f` takes as input the complete $(x, \theta)$ ($y$ is already fixed).
For example:

```{r}
param
f$fn(unlist(param))
```

We update `param` to include $\hat{\mu}_{-i}(x_i, \theta)$, so that it's only element `r i` of `phi_prev` which remains as before:

```{r}
param$phi_prev[-i] <- mean
param
```

The numerator of the Laplace approximation is (n.b. this is on the log-scale, which is where we will do the calculations):

```{r}
numer <- -1 * f$fn(unlist(param))
numer
```

And the denominator of the Laplace approximation (again on the log-scale) is:

```{r}
denom <- 0.5 * (determinant(Q, logarithm = TRUE)$modulus - (nrow(Q) * log(2 * pi)))
denom
```

```{r}
numer - denom
```

Compare this to the output from `obj`:

```{r}
-1 * obj$fn(transformed_param)
```

>>>>

For the `phi_prev` parameters, we compute their `mean` and `Q` using `h`.
We then we evaluate everything using `f` to get the numerator.
We multiply by -1 because `f$fn` gives the negative log-likelihood, and we want just the log-likelihood.
In the denominator, we use `determinant` on the log-scale as it is more numerically stable than e.g. `log(det(...))`.
On the log-likelihood scale, the number we get is:

```{r}
calculate_rhs <- function(theta) {
  #' Calculate mean and Q for those theta
  #' TMB template remembers what you've called -- spooky
  h$fn(theta)
  mm <- h$env$last.par
  mean <- mm[h$env$random]
  Q <- h$env$spHess(mm, random = TRUE)

  #' Append the calculated latent field mean
  param <- theta
  param$phi_prev <- as.numeric(mean)
  param <- param[c("beta_prev", "phi_prev", "log_sigma_phi_prev")]

  #' Evaluate the log-numerator of the RHS
  numer <- -1 * f$fn(unlist(param))

  #' Evaluate the log-denominator of the RHS
  denom <- 0.5 * (determinant(Q, logarithm = TRUE)$modulus - (nrow(Q) * log(2 * pi)))

  #' Return their difference
  numer - denom
}

theta <- param
theta$phi_prev <- NULL

calculate_rhs(theta)
```

@@

```{r}
-1 * h$fn(input_hyper)
```

@@
